Solving the power flow problem on integrated transmission-distribution networks: a review and numerical assessment

### 2020-02-06 IEEEtran/paper.tex
Uploaded tables

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.3}
\centering
\label{tab:resultsPIC3P}\hspace{2cm}
\begin{adjustbox}{width=1.2\textwidth} %, angle=90}
\small
\begin{tabular}{@{}l c cc c cc c cccc c cccc c cccc c cccc  @{}}\toprule
                               && \multicolumn{2}{c}{\textit{F3P}} &&     \multicolumn{2}{c}{\textit{IC}}     && \multicolumn{4}{c}{\textit{MS-homo-CAI}} && \multicolumn{4}{c}{\textit{MS-homo-MAI}}&& \multicolumn{4}{c}{\textit{MS-hybrid-CAI}}  && \multicolumn{4}{c}{\textit{MS-hybrid-MAI}}   \\ \toprule 
\multicolumn{1}{l}{}        && \textit{its}      & \textit{CPU}     && \textit{its}       & \textit{CPU}           && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}     &&$I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}  && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}  && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}      \\
\cmidrule{3-4}  \cmidrule{6-7} \cmidrule{9-12} \cmidrule{14-17} \cmidrule{19-22} \cmidrule{24-27}  
\multicolumn{1}{l}{}      && \textit{\#}       & \textit{sec}    && \textit{\#}       & \textit{sec}           && \textit{\#}      & \textit{\#}    & \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{\#}     &  \textit{\#}       & \textit{sec}  && \textit{\#}      & \textit{\#}   & \textit{\#}       & \textit{sec}  && \textit{\#}      & \textit{\#}    &  \textit{\#}       & \textit{sec}      \\
\toprule
\multicolumn{1}{l}{\textit{T9-D13 (7)}}      && 4 &\textbf{ 0.610} && 4 & {0.455 }  && 4 & 4 & 4 &  0.237 && 6       & 2 & 2  & \textbf{0.257}&& 4       & 4  & 4 & 0.308 && 6      & 2  & 2 & 0.323  \\
\multicolumn{1}{l}{\textit{T9-D37 (7)}}      && 4 & \textbf{0.587} && 4 & 0.464    && 3 & 4 & 4 &  0.262 && 6       & 2 & 2  & \textbf{0.299}&& 3      & 4  & 4 & 0.325 && 6      & 2  & 2 & 0.352  \\
\multicolumn{1}{l}{{\textit{T118-D13 (89)}}}   && 5 & \textbf{0.763} && 4 & 0.522    && 3       & 7 & 5  & 0.324 && 4*,3*,3   & 2*,3*,4 &2*,3*,4 &  0.297*,0.312*,0.294,0.321 && 3      & 7 & 5 & 0.348 && 4*,4*,3,3  & 2*,3*,4,5  & 2*,3*,4,5 & {0.312*}, 0.326*, 0.319, 0.319 \\
\multicolumn{1}{l}{{\textit{T118-D37 (89)}}}   && 5 & \textbf{0.920} && 4 & 0.518    && 3       & 7 & 5  & 0.360 && 4*,5*,3*,3*,3  & 2*,3*,4*,5*,6* & 2*,3*,4*,5*,5* &  0.325,0.368,0.323,0.351,0.347 && 3      & 7 & 5 & 0.356 && 4*,5,3,3,3  & 2*,3,4,5,6  & 2*,3,4,5,5 & {0.358*},0.380,0.353,0.354,0.351 \\
\multicolumn{1}{l}{{\textit{T3120-D37 (3003)}}}   && 5 & \textbf{2438} && 5 & 143   &&  3 & 6  & 4  & 1213  && 6 & 2 & 2 &  841   && 3      & 6  & 4  & 383 && 6*  & 2*  & 2* & {235*}  \\
% \multicolumn{1}{l}{\textit{T9-2D13}}       && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
% \multicolumn{1}{l}{{\textit{T9-3D13}}}    && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
\toprule 
\end{tabular}
\end{adjustbox}
\caption{Comparison on number of iterations (for the MSS-method ($I_{MSS}$) and the necessary iterations per system ($I_T$ and $I_D$)), and CPU-time of the four different MSS-methods, applied on five test-cases. The numbers marked with an asterisk converged to wrong results. In this case, the MAI method required more than 2 subiterations to converge correctly. The slowest CPU times are printed in bold.}
\end{table}
\newpage

>>>>

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.3}
\centering
\label{tab:resultsPIC3P}\hspace{2cm}
\begin{adjustbox}{width=1\textwidth} %, angle=90}
\small
\begin{tabular}{@{}l c cc c  cccc c cccc c  @{}}\toprule
                               && \multicolumn{2}{c}{\textit{IC}} &&     \multicolumn{4}{c}{\textit{MS-hybrid-CAI}} && \multicolumn{4}{c}{\textit{MS-hybrid-MAI}} \\ \toprule 
\multicolumn{1}{l}{}        && \textit{its}      & \textit{CPU} && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}     &&$I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}      \\
\cmidrule{3-4}  \cmidrule{6-9}  \cmidrule{11-14}   
\multicolumn{1}{l}{}      && \textit{\#}       & \textit{sec} && \textit{\#}      & \textit{\#}    & \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{\#}     &  \textit{\#}       & \textit{sec}  \\
\midrule
\multicolumn{1}{l}{\textit{T9-D13 (7)}}         && 4 & {0.455 } && 4       & 4  & 4 & 0.308 && 6      & 2  & 2 & 0.323  \\
\multicolumn{1}{l}{\textit{T9-D37 (7)}}         && 4 & 0.464    && 3      & 4  & 4 & 0.325 && 6      & 2  & 2 & 0.352  \\
\multicolumn{1}{l}{{\textit{T118-D13 (89)}}}    && 4 & 0.522    && 3      & 7 & 5 & 0.348 && 4 & 2  & 2 & {0.312*} \\
\multicolumn{1}{l}{{\textit{T118-D37 (89)}}}    && 4 & 0.518    && 3      & 7 & 5 & 0.356 && 4 & 2  & 2 & {0.358}\\
\multicolumn{1}{l}{{\textit{T3120-D37 (3003)}}} && 5 & 143      && 3      & 6  & 4  & 383 && 6*  & 2*  & 2* & {235*}  \\
% \multicolumn{1}{l}{\textit{T9-2D13}}       && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
% \multicolumn{1}{l}{{\textit{T9-3D13}}}    && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
\toprule 
\end{tabular}
\end{adjustbox}
\caption{Comparison on number of iterations for hybrid networks (for the MSS-method ($I_{MSS}$) and the necessary iterations per system ($I_T$ and $I_D$)), and CPU-time of the four different MSS-methods, applied on five test-cases. The numbers marked with an asterisk converged to wrong results. In this case, the MAI method required more than 2 subiterations to converge correctly. The slowest CPU times are printed in bold.}
\end{table}

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.3}
\centering
\label{tab:resultsPIC3P}\hspace{2cm}
\begin{adjustbox}{width=1\textwidth} %, angle=90}
\small
\begin{tabular}{@{}l c cc c  cccc c cccc c  @{}}\toprule
                               && \multicolumn{2}{c}{\textit{F3P}} &&     \multicolumn{4}{c}{\textit{MS-homo-CAI}} && \multicolumn{4}{c}{\textit{MS-homo-MAI}} \\ \toprule 
\multicolumn{1}{l}{}        && \textit{its}      & \textit{CPU} && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}     &&$I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}      \\
\cmidrule{3-4}  \cmidrule{6-9}  \cmidrule{11-14}   
\multicolumn{1}{l}{}      && \textit{\#}       & \textit{sec} && \textit{\#}      & \textit{\#}    & \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{\#}     &  \textit{\#}       & \textit{sec}  \\
\midrule
\multicolumn{1}{l}{\textit{T9-D13 (7)}}      && 4 &\textbf{ 0.610}  && 4 & 4 & 4 &  0.237 && 6       & 2 & 2  & \textbf{0.257}\\
\multicolumn{1}{l}{\textit{T9-D37 (7)}}      && 4 & \textbf{0.587}    && 3 & 4 & 4 &  0.262 && 6       & 2 & 2  & \textbf{0.299}\\
\multicolumn{1}{l}{{\textit{T118-D13 (89)}}}   && 5 & \textbf{0.763}     && 3       & 7 & 5  & 0.324 && 4  & 2 &2 &  0.297  \\
\multicolumn{1}{l}{{\textit{T118-D37 (89)}}}   && 5 & \textbf{0.920}    && 3       & 7 & 5  & 0.360 && 4 & 2 & 2 &  0.325 \\
\multicolumn{1}{l}{{\textit{T3120-D37 (3003)}}}   && 5 & \textbf{2438}   &&  3 & 6  & 4  & 1213  && 6 & 2 & 2 &  841    \\
% \multicolumn{1}{l}{\textit{T9-2D13}}       && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
% \multicolumn{1}{l}{{\textit{T9-3D13}}}    && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
\toprule 
\end{tabular}
\end{adjustbox}
\caption{Comparison on number of iterations for homogeneous networks (for the MSS-method ($I_{MSS}$) and the necessary iterations per system ($I_T$ and $I_D$)), and CPU-time of the four different MSS-methods, applied on five test-cases. The numbers marked with an asterisk converged to wrong results. In this case, the MAI method required more than 2 subiterations to converge correctly. The slowest CPU times are printed in bold.}
\end{table}
\newpage
\input{L-MAIN2}

\input{L-MAIN1}
\input{F3Pnorms}
\input{ICnorms}

\input{L-N2I1}
\input{L-N1I1}
\input{L-N2I2}
\input{L-N1I2}
\newpage
